%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Low Latency Engineer} % Job title
    {HSBC} % Organization
    {London, UK} % Location
    {Feb. 2020 - now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivering high-performance components of application infrastructure (data structures, parsers, shims, etc).}
        \item {Tuning software execution stack (HW, OS, JVM) for soft-realtime requirements.}
        \item {Leading yearly hardware refresh initiative (working with HW manufacturers, PoC evaluation).}
        \item {Designing and implementing tools for extracting and visualizing detailed metrics from the HW, kernel and the JVM.}
        \item {Evaluation and research into compiler control, GraalVM, techniques for keeping icache hot, data prefetching, etc.}
        \item {Code reviews for performance-critical software components, performance troubleshooting in production.}
        \item {Kernel driver- and OpenJDK hacking, replaced JDK's NIO subsystem with more capable and perfromant native equivalent}
        \item {Delivered PCAP replay for all production UDP streams and revolutionized approach to benchmarking application performance in UAT.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {High Performance Systems Specialist} % Job title
    {Morgan Stanley} % Organization
    {London, UK} % Location
    {Oct. 2018 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Advanced research into high performance systems innovation (PCIe-CPU core affinity, sub-numa, AVX thermals, Intel's CAT).}
        \item {Built high resolution event timing solution for realtime latency capture.}
        \item {Customizing HW-, OS- and JVM-level configuration to reduce latency and tame platform jitter.}
        \item {Implementing high performance native components for latency-sensitive Java code.}
        \item {Guiding and mentoring different teams and groups within Institutional Securities Division to help them achieve their performance goals.}
        \item {Resolving ongoing performance issues, driving latency-oriented capacity planning and resource partitioning.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Executive Director} % Job title
    {Goldman Sachs} % Organization
    {London, UK} % Location
    {May 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivered continuous metrics collection for all layers of software execution stack (built with OSS).}
        \item {Implemented perf and raw hardware event counter API for Java to precisely track code execution dynamics.}
        \item {Optimized Java code and managed runtime configuration to reduce memory access latency.}
        \item {Reduced deoptimization penalty in uncommon code paths with compiler control.}
        \item {Tuning hw- and os-level configuration for low latency (bios, openonload, sysctl, irq/workqueue affinity mask, tickless kernel).}
        \item {Implemented access to hardware RX timestamps from Java code.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Low Latency Software Specialist} % Job title
    {HSBC} % Organization
    {London, UK} % Location
    {Apr. 2016 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivered infrastructure and software monitoring platform offering insight into metrics for all layers of the technology stack: HW, OS, JVM, apps (InfluxDB, Telegraf, Grafana, Python).}
        \item {Implemented and integrated performance-sensitive core components across eFX space (high-resolution event timing, zero-allocation ultra-low latency FIX processor, branch-less numeric parsers, delta compression codecs).}
        \item {Evaluating low-latency integrated market access products.}
        \item {Performance troubleshooting across the whole estate (ftrace, perf, lttng, Java Mission Control, etc.).}
        \item {Tuning environments for low-latency applications (SolarFlare + OpenOnload, tickless kernels, IRQ balancing, optimal component layout vs NUMA topology).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Low Latency Java Developer} % Job title
    {Nomura International Plc} % Organization
    {London, UK} % Location
    {Aug. 2013 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Driving HFT innovation by leveraging mechanical sympathy and JVM expertise. Delivering high performance core components within ultra low-latency environment.}
        \item {Developed ultra low-overhead latency monitoring with near-realtime reporting.}
        \item {Designed and implemented gc-less and lock-free data structures (bytebuffer ring, Java off-heap flyweight objects).}
        \item {Developed low overhead latency monitoring with near-realtime reporting.}
        \item {Tuned and optimized kernel- and hw-level aspects of production environments in co-location sites.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {Clear2Pay} % Organization
    {Warsaw, Poland} % Location
    {Oct. 2012 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automating payment processing smoke tests (Websphere 7, Jersey REST, Junit, JMS).}
        \item {Developing processing logic for Credit Transfer and Direct Debit for Royal Bank of Scotland.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Low Latency Developer} % Job title
    {UBS Investment Bank} % Organization
    {Zurich, Switzerland} % Location
    {Mar. 2012 - Oct. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimizations in the area of low latency communications, applying HPC techniques to implement high frequency trading standards (message processing within microsecond range).}
        \item {Developed zero-gc low latency market data and trading gateways based on FIX and/or proprietary protocols.}
        \item {Troubleshooting and GC-tuning UBS production environments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Managing Consultant} % Job title
    {PriceWaterhouseCoopers (former Outbox)} % Organization
    {Warsaw, Poland} % Location
    {Sep. 2011 - Mar. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performance troubleshooting in a whole range of enterprise Java systems from Outbox portfolio (telco industry).}
        \item {CPU and memory profiling and optimizations as well as code auditing and general design and implementation level advisory.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Java Developer} % Job title
    {LMAX} % Organization
    {London, UK} % Location
    {May 2011 - Sep. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing realtime FX trading platform with non-blocking algorithms and data structures.}
        \item {Building automated performance scoring solution used in CI}
        \item {Researching optimizations for LMAX disruptor.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Managing Consultant} % Job title
    {PriceWaterhouseCoopers (former Outbox)} % Organization
    {Warsaw, Poland} % Location
    {Jun. 2007 - May 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Key Account Manager - handling day-to-day business relations, team management, procuring RFIs and RFPs, project planning, resolving delivery issues, etc.}
        \item {Principal developer for a large portfolio of telco projects across a whole range of clients from France Telecom Group.}
        \item {Hands-on approach with contributions to a broad spectrum of systems ranging from Intelligent Network to customer verification to order validation and completion (Jboss, Drools, Hibernate, Spring, WS, SOA).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Developer} % Job title
    {Asseco (former ABG)} % Organization
    {Warsaw, Poland} % Location
    {Nov. 2004 - Jun. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {System analyst (state and acitivity flows and process definitions, use cases); implemented automated process definition generation from UML diagrams.}
        \item {Senior developer/team leader. Managing a team of 12 engineers, developing core components and business functionality in n-tier system, code reviews (Enterprise Architect, Weblogic, Hibernate)}
        \item {Core Team member.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
